\documentclass[a4paper, twoside]{NUSThesis}
\usepackage[
backend=biber,
style=nature,
%citestyle=numeric,
giveninits=true,
doi=false]{biblatex}
%\DeclareFieldFormat*{title}{``#1''\newunitpunct} % move comma outside the quotation mark
\addbibresource{references.bib}
\usepackage[PetersLenny]{fncychap}
%\ChNumVar{\fontsize{60}{70}\rm\textcolor[rgb]{.21, .34, .50}}
\renewcommand{\TL}[1]{\color[HTML]{888888}\setlength{\tl}{#1}}
\ChNameVar{\color[HTML]{888888}\fontsize{14}{16}\rm}
\ChNumVar{\fontsize{60}{62}\rm\color[HTML]{888888}}
\ChTitleVar{\huge\notosans\bfseries\color[HTML]{000000}}
%\ChTitleVar{\huge\bfseries\sf}
\usepackage{pkg_def}
\usepackage{thesis_sym}
\usepackage{calligra} % for dedication

\title{Modeling Nonlinear Optical Response in 2D materials from Nonequilibrium Quantum Dynamics}
\author{Wenwen Mao}
\prevdegrees{Universität Hamburg}
\degree{Erlangung des Doktorgrades}
\field{der Fakultät für Mathematik, Informatik und Naturwissenschaften, Fachbereich Physik}
\degreeyear{2024}

\supervisor{Professor Angel Rubio\\Associate Professor Shunsuke Sato}

% only involve the examiners in the final submission
\examiners{%
    Professor ????????????/\\
    Associate Professor ?????????\\
    Professor ???????, ??????????? University}

\hypersetup{
    pdfauthor={Wenwen Mao},
    pdftitle={Modeling Nonlinear Optical Response in 2D materials from Nonequilibrium Quantum Dynamics},
}

%\hyphenation{thatshouldnot}
%\usepackage[none]{hyphenat}
\begin{document}
\maketitle
\makedeclaration
\frontmatter

\begin{acknowledgments}

	Completing this thesis and attaining my PhD would have been impossible without the tremendous support of numerous individuals, whose guidance, encouragement, and patience have been invaluable to me.

	First and foremost, I extend my deepest appreciation to Prof. Dr. Angel Rubio for his exceptional supervision and unwavering patience throughout my doctoral journey. His passion for research and compassionate approach to mentorship not only enriched my scientific understanding but also left a profound impact on my approach to life.
	I am equally grateful to my co-supervisor Prof. Dr. Shunsuke Sato for his remarkable guidance and close mentorship. Prof. Sato's extraordinary physical intuition has continually astonished me, and many ideas within this thesis are a testament to his profound influence. His patience and steadfast support during challenging moments were instrumental in my journey to completing my PhD. I am profoundly grateful to my supervisors, for their unwavering support, invaluable guidance, and insightful feedback throughout every stage of this research endeavor. Their expertise and encouragement have been instrumental in shaping this thesis. I am especially grateful for his invaluable assistance during the final stages of thesis writing.

	I am indebted to the experimental cooperators Prof.Hideki Hirori and Dr. Kotaro Nakagawa from Kyoto University for his insightful discussions and suggestions during the HHG spectra project, which greatly enriched my understanding of the subject. Their proficiency in nonlinear opotical spectspecific specific experimental technique or methodology was instrumental in obtaining crucial data and insights. Special thanks are due to Prof. Dr. Kazuhiro Yabana for his invaluable insights and discussions, the visiting during my travels in Yabana's group in Tsukuba University, Japan provided cherished memories. Also thanks Prof. Peizhen Tang and Prof. Shin Dongbin for their detailed guidance and thank them for their explanation, support and guidance in the solid systems' computing techniques.

	I am grateful to the staff and resources of Max Planck Institute for the Structure and Dynamics of Matter (MPSD), whose facilities and assistance have facilitated the smooth progress of my research. Also to training opportunities from the International Max Planck Research School for Ultrafast Imaging \& Structural Dynamics (IMPRS) fellowship.

	To all my friends and colleagues who have supported and encouraged me along this journey, I extend my heartfelt gratitude. Your camaraderie and friendship have been a source of strength and inspiration.
	Above all, I owe an immense debt of gratitude to my family for their unwavering support and love throughout the years of my PhD. Their care and encouragement sustained me through the challenges, and I am forever grateful for their presence in my life.
\end{acknowledgments}
\clearpage
% \begin{dedication}
% 	\calligra \large To my
% \end{dedication}
% \clearpage
{
	\hypersetup{linkcolor=[rgb]{.21, .34, .50}}
\tableofcontents
\cleardoublepage
\begin{abstract}
	This thesis investigates the nonlinear optical response in 2D materials through a comprehensive examination of nonequilibrium quantum dynamics with in house developed tight binding model able to capture electron dynamics of open quantum systems. The first study explores the injection of nonlinear current in monolayer hexagonal boron nitride under two-color linearly-polarized laser fields, unveiling the breakdown of time-reversal symmetry and the emergence of ballistic current by solving time-dependent Schr\"odinger equation. In the second investigation, terahertz-induced high-order harmonic generation (HHG) and nonlinear electric transport in graphene are scrutinized, revealing the accurate modeling of electron dynamics through a nonequilibrium steady-state approach. Additionally, the third work delves into the enhancement of HHG in graphene by mid-infrared and terahertz fields with a join theoreticla and experiemntal study, attributing the phenomenon to a coherent coupling between MIR- and THz-induced transitions. We stress the validity of the theoretical framework developed in this thses in the analysis of nonlinear optical phenomena in materials, especially in microscopic pictures and dissipative non-equilibrium analysis; opening a new way for theoretical prediction. By synthesizing these findings, this thesis advances our understanding of nonlinear optical phenomena in 2D materials and underscores the significance of nonequilibrium quantum dynamics in modeling such intricate behaviors. Further extensions  of this work to other low dimensional phenomena in quantum materials are also highlighted in this report.
\end{abstract}
\cleardoublepage
\begin{abstraktum}
	Diese Dissertation untersucht die nichtlineare optische Reaktion in 2D-Materialien durch eine umfassende Untersuchung der Nichtgleichgewichtsquantendynamik mit einem intern entwickelten engen Bindungsmodell, das in der Lage ist, die Elektronendynamik offener Quantensysteme zu erfassen. Die erste Studie untersucht die Injektion von nichtlinearem Strom in einschichtiges hexagonales Bornitrid unter zweifarbigen linear polarisierten Laserfeldern und enthüllt den Zusammenbruch der Zeitumkehrsymmetrie und die Entstehung ballistischen Stroms durch Lösung der zeitabhängigen Schrödinger-Gleichung. In Die zweite Untersuchung befasst sich mit der Terahertz-induzierten Erzeugung von Harmonischen höherer Ordnung (HHG) und dem nichtlinearen elektrischen Transport in Graphen und zeigt die genaue Modellierung der Elektronendynamik durch einen Nichtgleichgewichts-Steady-State-Ansatz. Darüber hinaus befasst sich die dritte Arbeit mit der Verbesserung von HHG in Graphen durch mittlere Infrarot- und Terahertz-Felder mit einer gemeinsamen theoretischen und experimentellen Studie, die das Phänomen auf eine kohärente Kopplung zwischen MIR- und THz-induzierten Übergängen zurückführt. Wir betonen die Gültigkeit des in dieser Arbeit entwickelten theoretischen Rahmens bei der Analyse nichtlinearer optische Phänomene in Materialien, insbesondere in mikroskopischen Bildern und dissipativer Nichtgleichgewichtsanalyse, die einen neuen Weg für theoretische Vorhersagen eröffnen. Durch die Synthese dieser Erkenntnisse erweitert diese Arbeit unser Verständnis nichtlinearer optischer Phänomene in 2D-Materialien und unterstreicht die Bedeutung der Nichtgleichgewichtsquantendynamik bei der Modellierung solch komplexer Verhaltensweisen. Weitere Erweiterungen dieser Arbeit auf andere niederdimensionale Phänomene in Quantenmaterialien werden in diesem Bericht ebenfalls hervorgehoben.
\end{abstraktum}
% \listoftables
\listoffigures
\listofpublications
\begin{itemize}
	\item \textbf{Wenwen Mao}, Angel Rubio, Shunsuke A.~Sato. Nonlinear current injection in hexagonal boron nitride using linearly polarized light in a deeply off-resonant regime. (2024) {\it Advanced Optical Materials}, (Under Review)
	\item \textbf{Wenwen Mao}, Angel Rubio, Shunsuke A.~Sato. Enhancement of high-order harmonic generation in graphene by mid-infrared and terahertz fields. (2024) {\it Phys. Rev. B} 109 (4), 045421
	\item Kotaro Nakagawa, \textbf{Wenwen Mao}, Shunsuke A. Sato, Hideki Hirori, Hot electron effect on high order harmonic generation from graphene modulated by THz electric pulse fields. {\it APL Photonics}, (2024) (Under review)
	\item \textbf{Wenwen Mao}, Angel Rubio, Shunsuke A.~Sato. THz-induced high-order harmonic generation and nonlinear transport in graphene. (2022) {\it Phys. Rev. B} \textbf{106}, 024313
	\item Ofer Neufeld, \textbf{Wenwen Mao}, Hannes Hübener, Nicolas Tancogne-Dejean, Shunsuke A. Sato, Umberto De Giovannini, and Angel Rubio. Time- and angle-resolved photoelectron spectroscopy of strong-field light-dressed solids: Prevalence of the adiabatic band picture. (2022) { \it Phys. Rev. Research} \textbf{4}, 033101
\end{itemize}
}

\printglossary[type=symbols, style=long, title={List of Abbreviations}]
\mainmatter
%\include{chapter/background_theory}
\include{chapter/chapter1}
\include{chapter/chapter2}
\include{chapter/chapter3}
\include{chapter/chapter4}
\include{chapter/chapter5}
\include{chapter/chapter6}
\appendix
\include{chapter/A_adiabatic}

%\include{chapter/A_math}
\backmatter
\begingroup
\onehalfspacing
\printbibliography[heading=bibintoc]
\endgroup
\end{document}
